---
title: "DATA607_ASSIGNMENT3"
author: "Krishna Rajan"
date: "2/17/2018"
output:
  pdf_document: default
  html_document: default
---





##Copy the introductory example. The vector name stores the extracted names.
```{r}
library(stringr)
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
```
##(a) Use the tools of this chapter to rearrange the vector so that all elements conform to thestandardfirst_name last_name.




```{r}
name
fst_lst_name <- sub(" [A-z]{1}\\. ","",name)
fst_lst_name
fst_lst_name_final <- sub("(\\w+),\\s(\\w+)","\\2 \\1", sub("[A-z]{2,3}\\. ","",fst_lst_name))
fst_lst_name_final
data.frame(fst_lst_name_final)
```
##(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).
```{r}
str_detect(name, "[[:alpha:]]{2,3}[.]")
```
##(c) Construct a logical vector indicating whether a character has a second name.

```{r}
fst_lst_name_final
grepl ( ",",str_trim(fst_lst_name_final))
       
```
##4. Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.
##(a) [0-9]+\\$
```{r}
##$a. contains continous numbers followed by $ sign
ninenines <-"999999999$"
unlist(str_extract_all(ninenines, "[0-9]+\\$"))

```

##(b) \\b[a-z]{1,4}\\b
```{r}
##b. expression denotes a word with 1 to 4 lowercase alphabets
SNTCES <- ("Mary had a little lamb whose name was John ")
unlist(str_extract_all(SNTCES, "\\b[a-z]{1,4}\\b"))
```

##(c) .*?\\.txt$
```{r}
##c. A word preceding period and ending with .txt
newsntcs <- ("mary had a little lamb whose name was john.txt")
unlist(str_extract_all(newsntcs, ".*?\\.txt$"))
```

##(d) \\d{2}/\\d{2}/\\d{4}

```{r}
##d.Numbers in the pattern "2 numbers/2 numbers/4 numbers"
nmbrpttrn <- ("11/22/333 34/56/4444 55/66/99878")
unlist(str_extract_all(nmbrpttrn, "\\d{2}/\\d{2}/\\d{4}"))

```

##(e) <(.+?)>.+?</\\1>
```{r}
##e.evaluate start and end markup tags which are well formed
tags <- c(" <MAry>had a little/>","<lamb>whose</fleece>","<was>white</as snow>")
tags <- str_extract(tags, "<(.+?)>.+?</\\1>")
tags
```
##9.9. The following code hides a secret message. Crack it with R and regular expressions. Hint: Some of the characters are more revealing than others! The code snippet is also available in the materials at www.r-datacollection.com.clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo     d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5 fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr
```{r}
## observe the capital letters that pop up every where in the sentence what if we extract only capital letters?
decode <-("clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
     Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
     d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
     fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr")
decode_1 <-unlist(str_extract_all(decode,"[[:upper:].]{1,}"))

decode_2 <- str_replace_all(paste(decode_1, collapse = ''), "[.]", " ")
decode_2
```

